Trans-dimensional Bayesian Inference and Nested Sampling

### 2014-08-11 Documents/Talk/content.tex
DNest figure
Include dnest figure
Software

>>>>

\begin{frame}[t]{Diffusive Nested Sampling}
\begin{columns}[T]
\begin{column}{0.35\textwidth}
  \vspace{30pt}
  \begin{itemize}
  \setlength{\itemsep}{20pt}
  \item Replace the posterior distribution with a {\bf mixture of constrained priors}
  \item Can cross valleys
  \end{itemize}
\end{column}
\hfill
\begin{column}{0.5\textwidth}
  \hspace{50pt}
  \includegraphics[scale=0.4]{dnest.png}
\end{column}
\end{columns}
\end{frame}

\begin{frame}[t]{Diffusive Nested Sampling}
\begin{itemize}
\setlength{\itemsep}{20pt}
\item I've implemented the sinewave problem and the galaxy problem
\item The common features (what proposals to use?) are delegated to
a separate library called {\tt RJObject}
\item Uses birth-death MCMC, but exploring the DNS distribution, rather than
the (harder) posterior.
\end{itemize}
\end{frame}

\begin{frame}[t]{Software}
\begin{itemize}
\setlength{\itemsep}{20pt}
\item Diffusive Nested Sampling in C++
{\tt github.com/eggplantbren/DNest3}
\item Birth-death models in C++
{\tt github.com/eggplantbren/RJObject}
\item These are free software (GPLd).
\end{itemize}
\end{frame}
